---
title: "Homework 4"
author: "Tung Nguyen"
date: "March 9, 2020"
output: pdf_document
---


```{r load package}
knitr::opts_chunk$set(echo=FALSE, comment=NA)
```
## 3.1
```{r}
movies = read.csv('movies.csv', header = TRUE)
head(movies)

```

&nbsp;&nbsp;&nbsp;&nbsp;a. Model for 3 predictors of Box response:

E(Box) = $b_{0} + b_{1}Rate + b_{2}User + b_{3}Meta$

&nbsp;&nbsp;&nbsp;&nbsp;b. Write the estimated equation
```{r fit model}
movies.lm = lm(Box ~ Rate + User + Meta, data = movies)
summary(movies.lm)
```
 - $\bar{BOX} = -169.08 + 35.5Rate + 0.43User + 1.25Meta$

&nbsp;&nbsp;&nbsp;&nbsp;c. Interpret the parameter Rate

For an increase in user rating, there's a corresponding increase of 35 units in Box office receipts, when all other variables is held constant.

## 3.3 
&nbsp;&nbsp;&nbsp;&nbsp;a. 
```{r }
box.lm = lm(Box ~ Rate + User + Meta + Len + Win + Nom, data = movies)
summary(box.lm)
anova(box.lm)
```
The SSE = 32435
&nbsp;&nbsp;&nbsp;&nbsp;b.
```{r}
anova(movies.lm)
```
The SSE for model with 3 variables is: 32823

&nbsp;&nbsp;&nbsp;&nbsp;e. COmpare s and $R^2$ adjusted values of the two models:
```{r}
cat('Full model: s\n')
cat(sqrt(anova(box.lm)$`Mean Sq`))
cat('\nAdjusted R-squared:  0.8472\n')
cat(paste(rep('===',8),sep=''))
cat(paste('\nReduced model: s\n'))
cat(sqrt(anova(movies.lm)$`Mean Sq`))
cat('\nAdjusted R-squared:  0.8675')

```

## 4.8 Estimated Equation: $E(\widehat{Salary|Sex}) = 24697 - 3340Sex$

&nbsp;&nbsp;&nbsp;&nbsp;1. Describe the meaning of the estimated equation:

- The average salary for all faculty regardless of their sexes is 24697. When sex is taken into account, the male faculty, on average, makes $3340 more than their female counterpart.

&nbsp;&nbsp;&nbsp;&nbsp;2. additiional model: $E(\widehat{Salary|Sex}) = 24697 + 201Sex + 759Years$

[TODO] Ask Ellingson about this

## 5.
```{r load dataset}
BGS = read.table('BGSgirls.txt',header = TRUE)
head(BGS)
colnames(BGS)
plots = c("WT2", "HT2", "WT9", "HT9", "ST9", "Soma")
plot(~WT2+WT9+ST9+Soma, data=BGS)
```

